### 2023-09-22 sections/summary.tex
Update summary.tex

I am completing my DPhil (PhD) dissertation in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom. Before starting the DPhil in October 2019, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile. Moreover, I served as a lecturer at the Universidad de Santiago and Universidad de Chile and as a consultant for the United Nations Development Programme (UNDP).

My doctoral research is supervised by Professor Petra Schleiter and focuses on the causes and consequences of ministerial turnover in 12 Latin American presidential countries from the mid-1970s to date. My project integrates elements of the principal-agent theory to evaluate specific incentives and strategies of the actors in presidential systems, considering the regime’s institutional features. In my data-gathering process, I applied optical character recognition (OCR), natural language processing (NLP) and machine learning techniques to almost 50 years of press report archives. In addition, my empirical strategy employs propensity score matching methods, semiparametric competing risks models and instrumental-variable regressions.

My research is funded by the Chilean National Agency for Research and Development (ANID), the St Hilda’s College Muriel Wise Fund and the Postgraduate and Postdoctoral Award of the Society for Latin American Studies (SLAS).
\vspace{1mm}
\end{cvparagraph}

>>>>

\textcolor{black}{I am completing my DPhil (PhD) dissertation in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom. Before starting the DPhil in October 2019, I earned an MA (1st) in Political Science and a BA (2:1) in Government, both from the Universidad de Chile. Moreover, I served as a lecturer at the Universidad de Santiago and Universidad de Chile and as a consultant for the United Nations Development Programme (UNDP).}

\textcolor{black}{My doctoral research is supervised by Professor Petra Schleiter and focuses on the causes and consequences of ministerial turnover in 12 Latin American presidential countries from the mid-1970s to date. My project integrates elements of the principal-agent theory to evaluate specific incentives and strategies of the actors in presidential systems, considering the regime’s institutional features. In my data-gathering process, I applied optical character recognition (OCR), natural language processing (NLP) and machine learning techniques to almost 50 years of press report archives. In addition, my empirical strategy employs propensity score matching methods, semiparametric competing risks models and instrumental-variable regressions.}

\textcolor{black}{My research is funded by the Chilean National Agency for Research and Development (ANID), the St Hilda’s College Muriel Wise Fund and the Postgraduate and Postdoctoral Award of the Society for Latin American Studies (SLAS).}
\vspace{1mm}
\end{cvparagraph}
